API design for machine learning software: experiences from the scikit-learn project

### 2013-06-26 paper.tex
Cosmit in Matlab/R paragraph.

In comparison to specialized languages for numeric and statistical programming
such as \textsc{matlab} and R \citep{r},
the use of Python as a host language has the distinct advantage
that it is a \textit{general purpose} language:
it has strong language and standard library support for such tasks as
string handling/text processing, interprocess communication, networking
and many of the other tasks that many machine learning programs
(whether academic or commercial)
will have to perform ``on the side''.
In addition, third-party libraries are available for many other routine tasks.

>>>>

In comparison to specialized languages for numeric and statistical programming
such as \textsc{matlab} and R \citep{r},
the use of Python as a host language has the distinct advantage
that it is a \textit{general purpose} language:
it has strong language and standard library support for such tasks as
string/text processing, interprocess communication, networking
and many of the other tasks that machine learning programs
(whether academic or commercial) routinely need to perform.
However, \textsc{matlab} and R remain the preferred language of many
researchers. As such, much scientific software is still open-sourced primarily
in these two languages.
